Analysis of Bauer et al. (2023) bioRxiv: <br> Persistence

### 2023-07-04 R/model_check_fcs.Rmd
Update model_check

@@

@@

@@

@@

@@

@@

@@

@@

@@

Leave one out probability integral transform

```{r loo-pit}
p1 <- bayesplot::ppc_loo_pit_overlay(y, yrep1, lw = weights(loo1$psis_object)) + bayesplot::theme_default()
p2 <- bayesplot::ppc_loo_pit_overlay(y, yrep2, lw = weights(loo2$psis_object)) + bayesplot::theme_default()
p1 / p2
```

@@

### Forest plot (BARG 3.B/5.B)

>>>>

The blue line (observed value) should be in the center of the
distribution of 500 simulated data sets.

@@

The traces of the four chains should overlap each other.

@@

R-hat values should be lower than 1.1.

@@

ESS should be greater than 0.1.

@@

If the technical problem of divergent transitions occurs, points would
be highlighted in green.

@@

Autocorrelation should go down to zero very fast.

@@

The kernel density estimate of the observed data (dark line) compared
with estimates for 50 simulated data sets drawn from the posterior
predictive distribution (thinner and lighter lines). The dark line
should be near the simulated curves.

@@

The dark line (computed from the observed data) should be in the center
of the posterior predictive distribution.

@@

All Pareto-k estimates should be \< 0.7.

@@

Density of the computed leave one out probability integral transform
(LOO PIT; dark curve) compared with the posterior predictive
distribution (light curves). The LOO PIT curve should be within the
range of light curves.

```{r loo-pit, message = FALSE}
p1 <- bayesplot::ppc_loo_pit_overlay(y, yrep1, lw = weights(loo1$psis_object)) + bayesplot::theme_default()
p2 <- bayesplot::ppc_loo_pit_overlay(y, yrep2, lw = weights(loo2$psis_object)) + bayesplot::theme_default()
p1 / p2
```

@@

### Forest plot of effect sizes (BARG 3.B/5.B)

### 2023-07-04 R/model_check_persistence.Rmd
Update model_check

Leave one out probability integral transform

```{r loo-pit}
p1 <- bayesplot::ppc_loo_pit_overlay(y, yrep1, lw = weights(loo1$psis_object)) + bayesplot::theme_default()
p2 <- bayesplot::ppc_loo_pit_overlay(y, yrep2, lw = weights(loo2$psis_object)) + bayesplot::theme_default()
p1 / p2
```

@@

### Forest plot (BARG 2.B/5.B)

>>>>

Computed leave one out probability integral transform (LOO PIT; dark curve) versus the posterior predictive distribution (light curves). The LOO PIT curve should be within the range of light curves.

```{r loo-pit, message = FALSE}
p1 <- bayesplot::ppc_loo_pit_overlay(y, yrep1, lw = weights(loo1$psis_object)) + bayesplot::theme_default()
p2 <- bayesplot::ppc_loo_pit_overlay(y, yrep2, lw = weights(loo2$psis_object)) + bayesplot::theme_default()
p1 / p2
```

@@

### Forest plot of effect sizes (BARG 2.B/5.B)
